Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-26 journal/article.tex
Some notes
Transformation description

\item
RQ3: What are typical successes and challenges in a large-scale agile
     transformation process?

@@

@@

\subsubsection{Typical activities in the transformation}

Training

Use of external consultants

Coaching

Pilot program

Seminars, workshops, other public events

Agile community

@@

>>>>

\item
RQ3: What are typical challenges in a large-scale agile transformation?

\item
RQ4: What factors facilitate adopting of agile methods?

@@

The second research question was aimed to discover how the process of
transformation can be described.
We provide an answer to Research Question 2 in several parts. First the initial
states of organizations are described. Secondly, we present a two-axial model
for categorizing transformation types. In the rest of this section we discuss
typical arrangements that relate to the change process, such as how training is
arranged, how change is lead, and what investments are done.

The challenge of giving a generic description on how transformations proceed is
that every organization is unique, and further, publications tended to provide
more focused viewpoints rather than describing the transformation process
itself. Therefore it was not sensible to attempt constructing a detailed model
on how large organizations adopt agile methods.
Table \ref{table:transformation_descriptiontypes} presents types of insights
each primary source provided in relation to Research Question 2.

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.52\textwidth}
                     >{\raggedright\arraybackslash}p{0.40\textwidth} }
        How transformation is described   &  Primary sources  \\
        \midrule
        Narrative description of transformation process &
                P3, P5, P6, P9, P11, P12, P16, P18,
                P24, P27, P30, P36, P40, P41, P46   \\
        Application of agile methods seen from a specific viewpoint (e.g. coaching team) &
                P10, P13, P15, P19, P23, P32, P34,
                P39, P47, P48, P50, P52    \\
        Viewpoints of challenges and success factors  &
                P17, P20, P21, P29, P37, P38, P49   \\
        Discussion on establising large scale agile practices  &
                P7, P8, P31, P42, P43, P44, P45   \\
        Only brief discussion on transformation process  &
                P1, P2, P4, P14, P22, P25, P26, P28, P33, P35, P51  \\
        \bottomrule
    \end{tabular}
    \caption{The main theme of each primary source, relating to providing
             insights of the transformation process}
    \label{table:transformation_descriptiontypes}
\end{table}

@@

\subsubsection{Transformation activities}

During transformation periods organizations conducted activities aimed towards
creating change. Examples on such activities are piloting new models, seminars
and workshops, training, and coaching on new models.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.61\textwidth}
                     >{\raggedright\arraybackslash}p{0.31\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Pilot programs and other piloting   & 
                P6, P7, P8, P9, P10, P11, P14, P16, P18, P22, P23, P24,
                P27, P29, P36, P38, P40, P41, P43, P45, P46, P47  \\
        \bottomrule
    \end{tabular}
    \caption{Activities in the organization aiming to create change}
    \label{table:transformation_activities}
\end{table}

% Pilot programs

Pilot projects and programs were a common practice at the start of the
transformation. Piloting was discussed in half of the cases.

When?

How many?

What kind?

Reasons for piloting

Big bang + Piloting
[P11, P16, P18, P41]

\subsubsection{Investing in new structures in transformation}

Even if any activities aiming for transformation can be considered as
investments in themselves, the transformation process included investments in
some tangible entities. These investments were focused on enabling agile
software development. Typical investments were new management tools,
improvements in testing environments, and updating of the physical working
spaces.

@@

% S: Have social events (get-togethers, etc.)
% 
% * Management team event --> Investment
% * The transformation management team met in person --> Personal bonding
% * A common understanding of the principles --> Consistent implementation
% * Excursion and training
% [P11]
% 
% * It was seen beneficial that the coach team had an event
% * The team had been dispersed
% * Road trip
% [P23]
% 
% * Various social activities are given as example of improve team bonding
% * Ways to build trust --> Trust is needed
% * Team outings
% [P27]
% 
% * Learn the difference between functions and formal roles
% * Teams participated in learning games
% * Learning games created understanding for team dynamics in the agile environment
% [P40]
% 
% * Team competition-based events
% * Short events in the middle of the work week
% * Teams got excited when they were able to compete and demonstrate their own best practices
% * Teams got encouragement to tailor practices
% [P41]
